### 2024-01-12 inst/scripts/papertest.Rmd

```{r}
z=24
neutraltraitsParam=initNeutralTraitsPathways(z = z)

@@

adaptive traits and communities:
```{r}
km=1
ki=4
traits=initAdaptiveTraits(ki=ki,km=km,n=3) # this generate a table for 3 adaptive traits, with ki communities of full hunter-gathere and km of farmers
traits[1:ki,]=0
traits[5,]=1

@@

communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(n=sum(initcomus$size),age="random",community = communities),initNeutralTraits(sum(initcomus$size),z))
```

@@

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.01, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=initNeutralTraitsPathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 50
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
```

@@

```{r runpropersimu}
tstep=1000
a=Sys.time()
simuTest=modelVector(
    K=ki, m=1, b=0.2, r=0.01, rho=0, d=0.01, 
    maturity=18, endrepro=65, 
    population=population, 
    comus=initcomus, 
    tstep=tstep, 
    tp=neutraltraitsParam,
    age.threshold=20, 
    out=c("finalpop","finalcomus","traitsumary","popsize"), #this time we keep track of more things
    logging=c("time","done","visu"),
    beta=-1,
    ma=1,traitsid=paste0("t",1:z),F_Th = 100
)
print(Sys.time()-a)

@@

traitsfreq=simuTest$traitsumary/simuTest$popsize

pathways= c("in-law","horiz before","horiz after")
plot(1,1,ylim=c(0,1),xlim=c(0,1000),type="n",xlab="time",ylab="freq")
sapply(1:24,function(tr)lines(traitsfreq[,tr],col=tr))
par(xpd=NA)
legend(x=-9,y=1.5,lwd=4,col=1:4,legend=paste0("t",1:4),cex=1,bty="n")

>>>>

```{r}
z=24
neutraltraitsParam=generatePathways(z = z)

@@

adaptive traits and communities:
```{r}
km=2
ki=8
traits=initAdaptiveTraits(ki=ki,km=km,n=3) # this generate a table for 3 adaptive traits, with ki communities of full hunter-gathere and km of farmers
traits[1:ki,]=0
traits[(ki+1):(ki+km),]=1

@@

communities=unlist(lapply(seq_along(initcomus$size),function(i)rep(i,initcomus$size[i])))
population=cbind(newpop(n=sum(initcomus$size),age="random",community = communities),generateTraitsMatrix(sum(initcomus$size),z))
```

@@

```{r runburnin,warning=FALSE,message=FALSE,results='hold',cache=TRUE}
tstep=500
tpcomu=initcomus
tpcomu$occupation[,]=1
burnin=modelVector(
   K=ki, m=1, b=0.2, r=0, rho=0, d=0.04, maturity=18, endrepro=65, 
   population=population, 
   comus=tpcomu, 
   tstep=tstep, 
   tp=generatePathways(z = z) , #we recreate a temporary neutral trait table with no neutral transmission
   age.threshold=20, 
   out=c("finalpop","finalcomus"),   #we only want the final population
   beta=-1,
   logging=c("time"),ma=1,traitsid=paste0("t",1:z),F_Th = 100
)
population=resetIds(burnin$population)
initcomus$size=burnin$finalcomus$size
```

@@

```{r runpropersimu}
tstep=2500
a=Sys.time()
simuTest=modelVector(
    K=ki, m=1, b=0.02, r=0.01, rho=0, d=0.001, 
    maturity=18, endrepro=65, 
    population=population, 
    comus=initcomus, 
    tstep=tstep, 
    tp=neutraltraitsParam,
    age.threshold=20, 
    out=c("finalpop","finalcomus","traitsumary","popsize"), #this time we keep track of more things
    logging=c("time","done","visu","popsize"),
    beta=-1,
    vidfile="test",
    ma=1,traitsid=paste0("t",1:z),F_Th = 100
)
print(Sys.time()-a)

@@

traitsfreq=quickV$traitsumary

pathways= c("in-law","horiz before","horiz after")
plot(1,1,ylim=c(0,400),xlim=c(0,2500),type="n",xlab="time",ylab="freq")
sapply(1:24,function(tr)lines(traitsfreq[,tr],col=tr))
par(xpd=NA)
legend(x=-9,y=1.5,lwd=4,col=1:4,legend=paste0("t",1:4),cex=1,bty="n")
